Carryover effects in free recall reveal how prior experiences influence memories of new experiences

### 2022-12-26 paper/main.tex
added note to intro about potential framing adjustments...
title tweak
working on introduction (backing up progress)

\title{Carryover effects in free recall reveal how prior experiences influence memory for new experiences}
\author{Jeremy R. Manning\textsuperscript{1, *}, Andrew C. Heusser\textsuperscript{1, 2}, Kirsten Ziman\textsuperscript{1, 3},\\Emily Whitaker\textsuperscript{1}, and Paxton C. Fitzpatrick\textsuperscript{1}\\\textsuperscript{1}Dartmouth College\\\textsuperscript{2}Akili Interactive\\\textsuperscript{3}Princeton University\\\textsuperscript{*}Corresponding author: jeremy.r.manning@dartmouth.edu}

@@

% gap between "classic" free recall tasks and naturalistic (or real-world) memory tasks

>>>>

\title{Carryover effects in free recall reveal how prior experiences influence memories of new experiences}
\author{Jeremy R. Manning\textsuperscript{1, *}, Andrew C. Heusser\textsuperscript{1, 2}, Kirsten Ziman\textsuperscript{1, 3},\\Emily Whitaker\textsuperscript{1}, and Paxton C. Fitzpatrick\textsuperscript{1}\\\textsuperscript{1}Dartmouth College\\\textsuperscript{2}Akili Interactive\\\textsuperscript{3}Princeton University\\\textsuperscript{*}Corresponding author: jeremy.r.manning@dartmouth.edu}

@@

%NOTE: should we start with the naturalistic framing?  or would it be more effective and direct to
% jump right into free recall?  i've added some potentially useful text to boneyard.tex that could be
% pasted in with some tweaking.  some of the above text could also be moved to the discussion section.

% gap between "classic" free recall tasks and naturalistic (or real-world) memory tasks
Our understanding of how we form situation models and schemas, and how they
interact with our subjective experiences and memories, is constrained in
part by substantial differences in how we study these processes.  Situation models
and schemas are most often studied using ``naturalistic'' 
stimuli such as narratives and movies~\citep{CITES}.  In contrast, our
understanding of how we organize our memories has been most widely studied
using more traditional paradigms like free recall of random word lists~\citep{Kaha12}.
Because random word lists are unstructured by design, it is not clear if or how non-trivial
situation models might apply to these stimuli.
